Holomorphic field theories and higher algebra

### 2024-10-12 draft.tex
not sure what i did

\subsection{Reduction vs. chiralization}
\label{sec: red vs chiral}

@@

In the last few years,
there has a been a buzz of recent activity on the renormalization of holomorphic field theories.
Budzik, Gaiotto, Kulp, Wu, and Yu developed a strategy for proving that in a holomorphic quantum field theory,
certain graphs (called Laman graphs) do not produce divergences~\cite{BGKWY}.
The key idea is to combine the heat kernel analysis with the sort of compactifications that are used in the theory of configuration spaces.

Recently, Minghao Wang has extended this analysis to show that holomorphic field theories on $\C^n$ admit a regularization scheme that is divergence-free to \textit{all} orders in perturbation theory \cite{Wang}.
In other words, both topological and holomorphic field theories are completely free of the divergences present in typical quantum field theories!
We briefly recall the approach to this regulation scheme.

@@

In other words, divergences do not appear when constructing the perturbative quantization of {\em any} holomorphic field theory on~$\CC^d$.
(Similar results hold for topological-holomorphic theories~\cite{WangWilliams}.)

This result ensures the existence of myriad examples of the higher algebraic structures we've discussed:
it provides the analysis to quantize the kinds of examples from Section~\ref{sec: ex of theories} and hence to produce polydiscs algebras and factorization algebras.

\subsection{Anomalies that obstruct quantization}

The discussion so far concerned the analytic issues that are present when trying to make the path integral precise.
For some quantum field theories, like gauge theories, there is another issue that could prevent the theory from being well-posed:
these are called {\em anomalies}.
An anomaly measures the failure of the path integral to enjoy the same symmetries as the underlying classical field theory.
In gauge theory, for instance, the perturbative renormalization might not be gauge invariant, although the classical action functional is.
Specifically, the gauge variation of a particular Feynman graph integral may be nonzero---this leads to an anomaly in the quantum theory.
In topological theories, it is known that these sort of anomalies are absent.
For holomorphic theories, however, anomalies are present.
(Within the context of Costello's formalism for perturbative QFT,
these anomalies arise as obstructions to solving a Maurer-Cartan equation known as the quantum master equation.)

@@

The gauge variation of the two diagrams which contribute to the gauge anomaly are shown in Figure~\ref{fig:localization}.
The difference between these two diagrams is how we label the internal edges: in the first diagram they are labeled by $A-B$ fields and in the second they are labeled by $\beta-\gamma$ fields.
An anomaly can be represented by a (local) functional on the space of fields.
In each diagram at hand, this local functional depends only on the holomorphic gauge field~$A$ and has the form
\beqn
c \int \op{Tr}_V (A \wedge \del A \wedge \del A)
\eeqn
where $c$ is some nonzero constant and $V$ is some representation of $\lie{g}$.\footnote{In this example, the value of $c$ is the same for both diagrams.}
Specifically, we have:
\begin{itemize}
\item In the first diagram the representation $V$ is the adjoint representation. 
Thus, this expression vanishes when $\lie{g}$ is simple, e.g., when $\lie{g} = \lie{sl}(n)$.
\item In the second diagram the representation is that used in defining the $\beta\gamma$ system.
\end{itemize}
The sum 
\[
c \int \left(\op{Tr}_M (A \del A \del A) + \op{Tr}_V(A \del A \del A)\right)
\]
is the total anomaly for this field theory.
These anomalies of a holomorphic gauge theory on $\CC^2$ are holomorphic avatars of the Adler--Bell--Jackiw, or chiral, anomaly in ordinary gauge theory on~$\RR^4$.

In the case that $\lie{g}$ is simple (so that the first diagram does not contribute to the anomaly), 
there is an easy way to produce a non-anomalous holomorphic QFT: 
take $V$ to be a symplectic representation of the gauge Lie algebra $V = Q \oplus Q^*$, where $Q$ is any $\lie{g}$-representation.

@@

The class of supersymmetric theories closest to the Standard Model, however, has only $\cN=1$ supersymmetry.
There too Seiberg offered inspiring and powerful insights about SQCD ($\cN=1$ supersymmetric QCD),
and one of his leading contributions is referred to as {\em Seiberg duality}.
It has had a large impact in theoretical physics,
but the impact in mathematics is much more muted,
possibly due to the lack of a topological twist for any $\cN=1$ theory.\footnote{Although citations offer only coarse insight into impact, Seiberg's paper introducing the conjecture \cite{Seiberg} has over 1800 citations listed on Inspire but less than 60 citations listed on MathSciNet.}
Such theories do admit {\em holomorphic} twists, however, 
and so we explore here what holomorphic Seiberg duality might mean and what its consequences could be in mathematics.
In our opinion this direction could be quite fruitful and we welcome others to join us in exploring it.

We begin this section by describing the holomorphic twist of $\cN=1$ supersymmetric Yang--Mills theory,
and then we offer a holomorphic version of Seiberg duality, 
initially conjectured by Richard Eager.
We end by sketching how this duality, when compactified along Riemann surfaces,
should produce equivalences between different kinds of 2-dimensional B-model theories;
these reductions are related to work of Hori and Hori--Tong and its mathematical development, notably by Segal and collaborators~\cite{Hori, HoriTong, HMSegRen, ADS}.

@@

A standard maneuver used in physics is compactification:
given a field theory $\cT$ in $n$ dimensions, one takes compact ($n$-$k$)-manifold $N$ and produces a field theory $\cT_N$ in $k$ dimensions by studying $\cT$ on manifolds of the form $N \times \Sigma$, where $\Sigma$ is $k$-dimensional.
One then considers the push forward of the theory along the projection map $N \times \Sigma \to \Sigma$, to obtain a theory along $\Sigma$.
(A close cousin is dimensional reduction, where one restricts to solutions of the classical field theory that are constant along~$N$.)

We now apply this maneuver to holomorphic Seiberg duality:
by compactifying along a Riemann surface, we should generate a conjectural equivalence between two-dimensional field theories.
As we will see, this new conjecture resembles the Hori-Tong dualities that have led to Hori-mological mirror symmetry~\cite{Hori, HoriTong, HMSegRen}.

Consider a holomorphic theory defined on $\C^\times \times \C^\times$ 
and push forward along the map $\rho: \CC^\times \times \CC^\times \to \RR_{>0} \times \RR_{>0}$ 
that sends $(z_1,z_2)$ to $(|z_1|, |z_2|)$.
In other words, take the torus compactification of the holomorphic theory.
For a holomorphic factorization algebra $\cF$, 
the pushforward $\rho_* \cF$ contains a locally constant factorization algebra on $\RR_{> 0}^2 \cong \RR^2$ (in essence, by taking the Fourier modes on the torus fibers).
This locally constant factorization algebra corresponds to an $E_2$-algebra.\footnote{Recall Section~\ref{sec: red vs chiral}, where we compactified on a circle and then broke things up using Fourier modes. This construction extracted an associative ($E_1)$ algebra that is a Weyl algebra of a formal loop space from a holomorphic field theory on~$C^\times$.}

Let's start with holomorphic QCD and see what Seiberg duality would imply.
On the electric side, 
we have a two-dimensional holomorphic BF theory coupled to a complex two-dimensional $\beta\gamma$ system.
By itself, the $\beta\gamma$ system with target $\C^{NF}$ yields, by torus compactification, 
the topological B-model theory whose target is the formal double loop space~$L^2\C^{NF}$. 
The algebra of functions of this target space is $\cO(\C^{NF}) ((z))((w))$, 
where $z,w$ are formal loop parameters that we imagine as describing the winding of the two circles we have compactified. 
The dimensional reduction then picks out the constant modes along each circle, 
so we find a topological B-model with target $\C^{NF}$.
Similarly, holomorphic BF theory dimensionally-reduces to topological BF theory,
which can be viewed as the B-model with target the classifying space~$BGL(N)$.
In sum, the dimensional reduction of electric holomorphic QCD is the topological B-model with target the stack $\C^{NF} / GL(N)$.
As a derived mapping space, the moduli of solutions is given by
\beqn
{\rm Map}\left(\RR^2, T^*[1] \C^{NF} / GL(N)\right) .
\eeqn
Dimensional reduction of the factorization algebra of observables produces the $E_2$ algebra of (holomorphic) polyvector fields on the stack~$\C^{NF} / GL(N)$.

On the magnetic side the reduction is similar, except this time we must take into account the superpotential. 
What results is a Landau--Ginzburg B-model whose target is the stack
\beqn
\left(\C^{(F-N)F} / GL(F-N) \right) \times \C^{F^2} .
\eeqn
The first factor comes from the reduction of the dual quarks coupled to the dual gauge theory, and the second factor comes from the reduction of the mesons. 
The potential for the Landau--Ginzburg model is precisely the potential $\check{W}$ seen in~\eqref{eqn:checkW}.
This procedure produces an $E_2$ algebra by deforming the differential on the $E_2$ algebra of polyvector fields on the stack $\C^{(F-N)F} / GL(F-N) \times \C^{F^2}$, 
namely use the differential $\{\check{W},-\}$ where $\{-,-\}$ is the Schouten bracket.

Holomorphic Seiberg duality thus predicts an equivalence of two-dimensional topological field theories,
or at least of $E_2$-algebras.

\begin{conj*}
There is an equivalence of $E_2$ algebras between
\begin{itemize} 
\item the {\em electric} $E_2$ algebra of polyvector fields on the stack $\C^{NF} / GL(N)$, and 
\item the {\em magnetic} $E_2$ algebra of polyvector fields on the stack $(\C^{(F-N)F} / GL(F-N)) \times \C^{F^2}$ with differential~$\{\check{W},-\}$. 
\end{itemize}
\end{conj*}

@@

This conjectured equivalence resembles Hori-Tong dualities.
Note that it is often said that Hori-Tong dualities are like Seiberg dualities!
We hope that insights from the study of these dualities --- such as the deep work on homological projective duality \cite{KuzHPD, ThomasHPD, Perry} --- might apply here, and also feed back towards holomorphic Seiberg duality.

>>>>

\subsection{Reduction vs. chiralization}

@@

In the last few years,
there has a been a buzz of recent activity on the renormalization of holomorphic field theories.
In work of Budzik, Gaiotto, Kulp, Wu, Yu, a strategy for proving UV finiteness for certain graphs (called Laman graphs) at arbitrary genus in a holomorphic quantum field theory is developed \cite{BGKWY}.
\owen{I think the term "UV finiteness" is too physics-y, and I don't find it very illuminating even then.}
\brian{I think it would be more confusing to use a different term. But you can explain how it's the issue of `overlapping supports' of distributions; that is, it's an issue about `local integrability'. In fact, in their work Axelrod and Singer already use the term ultraviolet.}
\owen{I agree that UV is a term many people use, but not among most of our target audience, which I view as algebraic geometers and higher algebra folks. Why not just say that we're showing no divergences appear and hence counterterms are not needed?}
The key idea is to combine the heat kernel analysis with the sort of compactifications that are used in the theory of configuration spaces.

Recently, Minghao Wang has extended this analysis to show that holomorphic field theories on $\C^n$ admit a regularization scheme that is UV finite to \textit{all} orders in perturbation theory \cite{Wang}.
In other words, both topological and holomorphic field theories are completely free of the divergences present in typical quantum field theories!
We briefly recall the approach to this regulation scheme.

@@

In other words, divergences do not appear when constructing the perturbative quantization of {\em any} holomorphic field theory on~$\CC^d$.
(Similar results hold for topological-holomorphic theories~\cite{WangWilliams}.)
Thus, using the quantization of holomorphic field theories 
\subsection{Anomalies that obstruct quantization}

The discussion so far concerned the analytic issues that are present when trying to make the path integral precise.
For some quantum field theories, like gauge theories, there is another issue that could prevent the theory from being well-posed:
these are called {\em anomalies}.
An anomaly measures the failure of the path integral to enjoy the same symmetries as the underlying classical field theory.
In gauge theory, for instance, the perturbative renormalization might not be gauge invariant, although the classical action functional is.
Specifically, the gauge variation of a particular Feynman graph integral may be nonzero---this leads to an anomaly in the quantum theory.
In topological theories, it is known that these sort of anomalies are absent.
\owen{I am confused by this comment. Aren't there TFTs with anomalies of some sort?}
For holomorphic theories, however, anomalies are present.
(Within the context of Costello's formalism for perturbative QFT,
these anomalies arise as obstructions to solving a Maurer-Cartan equation known as the quantum master equation.)

@@

The gauge variation of the two diagrams which contribute to the gauge anomaly are shown in Figure~\ref{fig:localization}.
The difference between these two diagrams is how we label the internal edges: in the first diagram they are labeled by $A-B$ fields and in the second they are labeled by $\beta-\gamma$ fields.
An anomaly can be represented by a (local) functional on the space of fields.
In each diagram at hand, this local functional depends only on the holomorphic gauge field~$A$ is of the form
\beqn
c \int \op{Tr}_M (A \del A \del A)
\eeqn
where $c$ is some nonzero constant and $M$ is some representation of $\lie{g}$ (the value of $c$ is the same for both diagrams, in this example).
Specifically:
\begin{itemize}
\item In the first diagram the representation $M$ is the adjoint representation. 
So, this expression vanishes when $\lie{g}$ is simple, e.g., for $\lie{g} = \lie{sl}(n)$.
\item In the second diagram the representation is $M = V$ (the representation which labels the $\beta\gamma$ system).
\end{itemize}
Thus, the total anomaly is $c \int \left(\op{Tr}_M (A \del A \del A) + \op{Tr}_V(A \del A \del A)\right)$.

These anomalies of a holomorphic gauge theory on $\CC^2$ are holomorphic avatars of the Adler--Bell--Jackiw, or chiral, anomaly in ordinary gauge theory on $\RR^4$ \cite{??}.
In the case that $\lie{g}$ is simple (so that the first diagram does not contribute to the anomaly), 
there is an easy way to produce a non-anomalous holomorphic QFT: 
take $V$ to be a symplectic representation of the gauge Lie algebra $V = Q \oplus Q^*$, where $Q$ is any $\lie{g}$-representation.

\owen{Owen's comments that I've tried to address:
\begin{itemize}
\item There isn't a $K$-edge on the wheel?
\item Should we just write out the formulas? What we write is kind of hard to parse, as it is shorthand. I can imagine a person asking "proportional ... how?".
\end{itemize}
}

@@

The class of supersymmetric theories closest to the Standard Model, however, has only $\cN=1$ supersymmetry.
There too Seiberg offered inspiring and powerful insights about SQCD ($\cN=1$ supersymmetric QCD),
and one of his leading contributions is referred to as {\em Seiberg duality}.
It has had a large impact in theoretical physics \owen{give the citation number on that paper},
but the impact in mathematics is much more muted,
possibly due to the lack of a topological twist for any $\cN=1$ theory.
Such theories do admit {\em holomorphic} twists, however, 
and so we explore here what holomorphic Seiberg duality might mean and what its consequences could be in mathematics.
In our opinion this direction could be quite fruitful and we welcome others to join us in exploring it.

We begin this section by describing the holomorphic twist of $\cN=1$ supersymmetric Yang--Mills theory,
and then we offer a holomorphic version of Seiberg duality, 
initially conjectured by Richard Eager.
We end by sketching how this duality, when compactified along Riemann surfaces,
should produce equivalences between different kinds of 2-dimensional B-model theories;
these reductions are related to work of Hori and Hori--Tong \owen{citations} and its mathematical development by Ed Segal, \owen{list others}.

@@

A standard maneuver used in physics is compactification:
given a field theory $\cT$ in $n$ dimensions, one takes compact $n-k$-manifold $N$ and produces a field theory $\cT_N$ in $k$ dimensions by studying $\cT$ on manifolds of the form $N \times \Sigma$, where $\Sigma$ is $k$-dimensional.
One then considers the push forward of the theory along the obvious map $N \times \Sigma \to \Sigma$, to obtain an effective theory along $\Sigma$.
A close cousin is dimensional reduction, where one restricts to solutions of the classical field theory that are constant along $N$.

We consider a holomorphic theory defined on $\C^\times \times \C^\times$ and the pushforward along the map $\rho: \CC^\times \times \CC^\times \to \RR_{>0} \times \RR_{>0}$ that sends $(z_1,z_2)$ to $(|z_1|, |z_2|)$.
In other words, this is the $T^2$ compactification of the holomorphic theory.
For a holomorphic factorization algebra $\cF$, one can extract from the pushforward $\rho_* \cF$ a locally constant factorization algebra on $\RR_{> 0}^2 \cong \RR^2$, hence an $E_2$-algebra.
We now apply this result in the context of holomorphic QCD and see what Seiberg duality would imply.

Let's first consider the electric side, 
which can be seen as two-dimensional holomorphic BF theory to a complex two-dimensional $\beta\gamma$ system.
The $T^2$ compactification of the $\beta\gamma$ system with target $\C^{NF}$ is the topological B-model theory whose target is the formal double loop space $L^2\C^{NF}$. 
The algebra of functions of this target space is $\cO(\C^{NF}) ((z))((w))$, 
where $z,w$ are formal loop parameters that we imagine as describing the winding of the two circles we have compactified. 
The dimensional reduction simply picks out the constant modes along each circle, so we find a linear topological B-model with target $\C^{NF}$.
Similarly, the dimensional reduction of holomorphic BF theory is topological BF theory (which is a stacky version of the B-model whose target is the classifying space $BGL(N)$).
In sum, the dimensional reduction of the electric holomorphic QCD is the topological B-model whose target is the stack $\C^{NF} / GL(N)$.
As a derived mapping space, the moduli of solutions is given by
\beqn
{\rm Map}\left(\RR^2, T^*[1] \C^{NF} / GL(N)\right) .
\eeqn
The factorization algebra of observables obtained from reduction encodes the $E_2$ algebra of (holomorphic) polyvector fields on the stack~$\C^{NF} / GL(N)$.

On the magnetic side the reduction is similar, except this time we must take into account the superpotential. 
What results is a Landau--Ginzburg B-model whose target is the stack
\beqn
\C^{(F-N)F} / GL(F-N) \times \C^{F^2} .
\eeqn
The first factor comes from the reduction of the dual quarks coupled to the dual gauge theory, and the second factor comes from the reduction of the mesons. 
The potential of the Landau--Ginzburg model is given by the same expression $\check{W}$ as in~\eqref{eqn:checkW}.

Holomorphic Seiberg duality then predicts an equivalence of two-dimensional topological field theories,
or at least of $E_2$-algebras.

\begin{conj}
There is an equivalence of the following $E_2$ algebras:
\begin{itemize} 
\item (electric) the $E_2$ algebra of polyvector fields on the stack $\C^{NF} / GL(N)$, and 
\item (magnetic) the $E_2$ algebra that results from deforming the $E_2$ algebra of polyvector fields on the stack $\C^{(F-N)F} / GL(F-N) \times \C^{F^2}$ by the differential $\{\check{W},-\}$ where $\{-,-\}$ is the Schouten bracket.
\end{itemize}
\end{conj}

@@

This conjectured equivalence resembles Hori-Tong dualities \cite{HoriTong, Hori, others}.
(In those papers, it is often said that Hori-Tong dualities are like Seiberg dualities!)
We hope that insights from the study of these dualities --- such as the deep work on homological projective duality \cite{Kuznetsov, Thomas, Segal, others} ---- might apply here, and also feed back towards holomorphic Seiberg duality.
For instance, in this mathematical work, 
one sees different choices of GIT quotients associated to the same stack yielding equivalent derived categories (and cousins),
and these quotients only know about certain pieces of the stack,
an issue we have flagged in our comparison of the moduli stack and the moduli space.
